\documentclass[letterpaper,10pt]{article}
\usepackage{hyperref}
% \usepackage{usenix}
% \usepackage[a4paper,margin=1.2in,rmargin=1.2in]{geometry}  %This should be removed before submission
\pagestyle{plain}

\newif\ifWorkInProgress
%\WorkInProgresstrue
\WorkInProgressfalse

%-------------------------------------------------------------------------------
\input{sty/packages}  %<-------------- Add new packages here
\input{sty/macros}
\input{sty/notation}
\input{sty/treekem-macros}
\crefname{appendix}{App.}{Apps.}%
\crefname{section}{Sec.}{Secs.}%
%-------------------------------------------------------------------------------
\title{Major Revision Changelog for ``Server-Aided Continuous Group Key Agreement''}

%for single author (just remove % characters)
\author{
% {\rm Joël Alwen}\\
% AWS Wickr
% \and
% {\rm Dominik Hartmann}\\
% Ruhr-University Bochum
% \and
% {\rm Eike Kiltz}\\
% Ruhr-University Bochum
% \and
% {\rm Marta Mularczyk}\\
% Department of Computer Science,	ETH Zurich
% copy the following lines to add more authors
% \and
% {\rm Name}\\
%Name Institution
} % end author

% hyperref doesn't like the LNCS author definition with pdfusetitle, do it manually
% \makeatletter
\hypersetup{
	pdftitle={\@title},
	pdfauthor={}
}
% \makeatother


\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}


\begin{document}
%\maketitle
{
	\def\addcontentsline#1#2#3{}
	\maketitle }

The paper has undergone one major revision. This was done after it was
submitted (and rejected) from Eurocrypt 2022. The major changes are as
follows:
\begin{itemize}
\item Removed ``reducible signatures'' from the paper entirely. Instead we
    found a better way to authenticate packets (namely by signing the
    confirmation tag). Not only does that reduce bandwidth for all parties,
    it also makes the protocol (and proof) quite a bit simpler.  We adapted
    the protocol and proof accordingly.
\item We restructured the paper as this was the main concern of the initial
    reviews from Eurocrypt. We did not receive the final (post-rebuttal)
    reviews from Eurocrypt by the time we submitted this version (although
    we did receive the rejection notification).
\item Repositioning of paper. (New abstract, intro.) New version more
    clearly describes changes to novel parts of our CGKA definition (e.g.
    introducing semantic security) and the reasons and consequences
    thereof. It also compares to the concurrent work
    of~\cite{hashimoto2021cmpke}.
\item One change we did \emph{not} make despite request from one reviewer
    is to include correctness in our formal definition. Since the beginning
    formal work on CGKA has consistently struggled to balance complexity
    with precision. Most past works have opted to capture as many
    intuitively desirable guarantees as possible. While this was achieved
    (e.g. in~\cite{EPRINT:AlwJosMul20}) it has also lead to consistent
    criticism of the resulting complexity and presented a significant
    barrier to entry in the field.

    To address this, in this work we have adhered to the principle of
    focusing the formalism as much as possible on the novel and non-trivial
    aspects of our work. Thus we intentionally omit correctness guarantees
    (from our formal notion only), as it is a property that is well
    understood, straightforward (if tedious) to define. Moreover,
    correctness is intuitively clear and easy to verify by inspection for
    our main construction. Based on this, we felt that satisfying this
    request would detract from the quality of this write-up.
\end{itemize}
% \renewenvironment{abstract}{%
% 	\list{}{\advance\topsep by0.75cm\relax\small
% 		\leftmargin=20mm
% 		\labelwidth=5mm
% 		\listparindent=5mm
% 		\itemindent\listparindent
% 		\rightmargin\leftmargin}\item[\hskip\labelsep
% 	\bfseries\abstractname]}
% {\endlist}

%\newpage
%\tableofcontents
%\newpage

%\listoftodos


%--- Bibliography --------------------------------------------------------------
\bibliographystyle{plain} %if need be use {plain}
%\bibliographystyle{splncs04}
\bibliography{project,../cryptobib/abbrev3,../cryptobib/crypto}


%--- Appendix ------------------------------------------------------------------
\clearpage
\newpage
\appendix


\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
