% !TEX root = main.tex
% !TeX spellcheck = en_US

\section{Details of \saik} \label{sec:saik-details}
\input{fig_state}
In this section we give the details of the \saik protocol. The pseudocode can be found in \cref{fig:prot1,fig:prot-helpers2}.

\subsection{Ratchet Trees}
\input{prot_ratchet_tree}

\subsection{\saik State and Algorithms}
\input{prot_state}

%\subsection{\saik Algorithms}
\saik's algorithms are defined in \cref{fig:prot1,fig:prot-helpers2}. Apart from initialization, there are three main algorithms (the rest of the code are subroutines) exposed to a user (or a higher-level application). They are identified by keywords \keyword{Send}, \keyword{Receive} and \keyword{Key}, respectively. First, \keyword{Send} is used to create a new epoch. When the user inputs \keyword{Send} followed by the intended group modification (update, add or remove), the protocol applies the modification and returns a message, which the user can upload to the mailboxing service. Second, \keyword{Receive} is used to process messages downloaded from the service. Third, with \keyword{Key} user gets the current group key.

The formal syntax of saCGKA protocols is defined as part of our security definition in \cref{sec:model}. In particular, an saCGKA protocol must expose the same interface as the ideal CGKA functionality.

\input{fig_prot}

\newcommand{\extract}{\method{extract}}
\newcommand{\getExtractionIndices}{\method{getExtractionIndices}}
\subsection{Extraction Procedure for the Server}
Finally, we describe a procedure $\extract(C, \id) \to c$ used by the mailboxing service to take an uploaded message $C$
and compute the message $c$ delivered to user $\id$. Formally, this procedure is not part of our syntax or security
definitions, since for simplicity our model does not consider correctness (see \cref{sec:simplifications}) and an
untrusted service can anyway deliver arbitrary messages. It is formally defined in \cref{fig:saik-extraction-alg}.

\input{fig_extract_alg}

Recall that $C$ contains the executed group operation $\hgact$ and the sender $\id_s$, a multi-recipient ciphertext $Ctxt$ and a vector of updated public keys $\updatedPks$. Roughly, $\extract$ only needs to compute $\id$'s individual mmPKE ciphertext $\mmpkeExtL(Ctxt, i)$ and the prefix of the first $j$ elements of $\updatedPks$. This requires that it knows the indices $i$ and $j$ for $\id$.
%
We notice that they can be easily computed using the public part of the ratchet tree, $\hgact$ and $\id_s$. Therefore, the indices can be obtained in two ways. First, the service can send $\hgact$ and $\id_s$ to $\id$, who replies with $i$ and $j$.  This requires interaction, but both $\id$ and the service are online at the time. Second, the service can store the current ratchet trees and compute $i$ and $j$ itself. The disadvantage of this is that it requires keeping a large state --- in case members are out of sync (e.g. a user is 10 epochs behind), the service needs to store one tree for each epoch which has an active member in it.
%
Once $i$ and $j$ are known, $\extract$ works as follows.

If $\hgact = \hglu$, set  $ctxt = \mmpkeExtL(Ctxt, i)$ and $\redactedUpPks = (\updatedPks[1], \dots, \updatedPks[j])$. Output $c =  (\id_s, \hgact, \pathSecCtxtInd,\allowbreak  \redactedUpPks,\allowbreak  \sig)$, where $\sig$ is a field of $C$. If $\hgact = \hglr\md\id$, then output $c =  (\id_s, \literal{removed}, \sig_t, \macsig_t)$ where $ \sig_t$ and $\macsig_t$ are taken from $C$. Finally, if $\hgact = \hgla\md\id$, $C$ contains $\variable{welcomeData}$, which in turn contains a ratchet tree. Based on this, compute $\id$'s index $i$ in $Ctxt$,  the number $n$ of recipients of $Ctxt$, and $ctxt_1 = $ $\mmpkeExtL(Ctxt, i)$ and $ctxt_2 = \mmpkeExtL(Ctxt, n+1)$. Output $c =  (\id_s, \hgact, \encGroupSecret_1,\allowbreak  \encGroupSecret_2,\allowbreak  \variable{welcomeData})$.

\subsection{Propose-Commit Syntax}
As discussed in \cref{sec:simplifications}, in order to tame the complexity of (sa)CGKA, we use a simplified syntax instead of the more general (and more efficient) propose-commit syntax. In this section we explain in detail how to transform \saik to the propose-commit syntax.

In the propose-commit syntax, an (sa)CGKA protocol takes the following inputs from a party $\id$:
\begin{description}
	\item[Add proposal:] $\id$ proposes to add $\id_t$. The protocol outputs a proposal packet $p$.
	\item[Remove proposal:] $\id$ proposes to remove $\id_t$. The protocol outputs a proposal packet $p$.
	\item[Update proposal:] $\id$ proposes to update their key material. The protocol outputs a proposal packet $p$.
	\item[Commit:] $\id$ inputs a list of proposal packets $(p_1, \dots, p_n)$ (after receiving them from other parties). The protocol outputs a commit packet $c$.
	\item[Process:] $\id$ inputs a commit packet $c$ and a list $(p_1, \dots, p_n)$ of proposals it commits (after receiving all these packets from other parties). The protocol outputs the semantics of applied group operations.
	\item[Key:] $\id$ fetches the current group key.
\end{description}

Observe that if an application always commits a single proposal immediately after creating it, the propose-commit syntax collapses to our (sa)CGKA syntax.

\paragraph{Proposals in \saik.}
\saik deals with proposals in the same way as \protITK. First, it computes the proposal content $\hgact$ which identifies the proposed modification:
\begin{description}
	\item[Add proposal:] To add $\id_t$, query $(\keyword{GetPk},\id_t) \text{ to } \funcKB$, receive $(\mmpkepk_t, $ $\rsvk_t, \mmpkepk_t')$ and set $\hgact = \literal{add}\md\id_t\md(\mmpkepk_t, \rsvk_t, \mmpkepk_t')$.
	\item[Remove proposal:] To remove $\id_t$, set $\hgact = \literal{rem}\md\id_t$.
	\item[Update proposal:] Sample new key pairs  $(\rsvk, \rssk) \gets \sigkg()$ and $(\mmpkepk, \mmpkesk) \gets \mmpkeKeyGenL()$ and store $\mmpkesk$ and $\rssk$ for later. Set $\hgact = \literal{upd}\md(\mmpkepk, \rsvk)$.
\end{description}
The proposal packet is $\hgact$ signed with the sender's current key $\gamma.\leaf(\id).\rssk$ and MACed with the current $\membershipKey$.

\paragraph{Commit in \saik.}
A commit in \saik is almost identical to its \keyword{Send} input. It proceeds in two steps.
\begin{enumerate}
	\item {\it Applying proposed group modifications to the ratchet tree:} Currently, \saik applies only a single modification in the $\createEpoch$ helper. The propose-commit \saik extends this step and applies all proposed actions one by one. This is done by calling the helper $\applyact(\itkSt', \id_s, \hgact)$ for each $\hgact$ (after verifying the signature and the MAC). Further, we extend the $\applyact$ helper to deal with update proposals -- such actions simply replace proposer's leaf public keys with the ones in $\hgact$. In addition, if the update proposal is applied by its sender, they replace their leaf's secret keys by $\mmpkesk$ and $\rssk$ stored when generating the update.
	\item {\it Rekeying the sender's path:} The remaining part of \keyword{Send} remains mostly unchanged. The only difference is related to the possibility of there being many add proposals:
	\begin{itemize}
		\item In line 9 of \keyword{Send} (excluding comments), the $\joinerSecret$ is currently encrypted to one new member. In the propose-commit \saik, it is instead encrypted to $N$ new members, who are the last $N$ recipients of the mmPKE ciphertext.
		\item In line 18 of \keyword{Send}, \saik currently computes the welcome data needed by new members. In the propose-commit \saik, this includes the public keys $(\mmpkepk'_1, \dots,$ $\mmpkepk'_N)$, of all $N$ new members, instead of only one. 
	\end{itemize} 
\end{enumerate}

\paragraph{Processing a commit in \saik}
The receive procedure of \saik is modified analogous to its send procedure. In case the receiver is a member and is not removed, it applies all proposed actions and then processes the committer's path exactly like the current \saik.

Finally, to join, a new member finds their public key in the list $(\mmpkepk'_1, \dots,\mmpkepk'_N)$ contained in the welcome data. Let $i$ denote the index of that key. They decrypt the $\joinerSecret$ as the $(N-i)$-th to last recipient of the mmPKE ciphertext. Then they proceed as in the current \saik.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
